PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-10-15 qfenv_paper/qf_environment.tex
blanton edits

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael~Blanton\altaffilmark{1}, 
Alison~Coil\altaffilmark{2}, 
Richard~Cool\altaffilmark{3}, 
Daniel Eisenstein\altaffilmark{4},
John Moustakas\altaffilmark{5}, 
Ken Wong\altaffilmark{6}, 
Guangtun Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{3}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{5}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from the PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Our stellar mass limited galaxy sample consists of $\sim 13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent or star-forming based on an evolving specific star formation cut, and as low or high density environments based on fixed cylindrical aperture environment measurements on a volume-limited Environment Definition Population (from PRIMUS and SDSS). For quiescent and star-forming galaxies in low or high density environments, we examine the evolution of their stellar mass function (SMF) evolution. Then using the SMFs we compute the $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify the evolution of $f_{\rm{Q}}(\mathcal{M}_{*})$ within our redshift range. We find that in both low and high density environments the quiescent fraction increases with cosmic time. Moreover, we illustrate that galaxy populations in high density environments have significantly higher quiescent fractions than galaxy populations in low density environments. Furthermore, by comparing the quiescent fraction evolutions in the environments, we find that the quiescent fraction evolves noticeably more for galaxy populations in high density environments. These results suggest that environment dependent quenching has a moderate effect on the quiescent fraction evolution. Furthermore our results provide constraints on the effect of environment on star-formation quenching.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest mass ($<10^{9}$ $M_\odot$) galaxies are quenched only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

@@

The most dramatic change in galaxy properties during the past eight
billion years has been a remarkable decline in the star-formation rate
of galaxies in the Universe (\citealt{hopkins06a}).  This decline
appears dominated by decreases in the rates of star-formation of
individual galaxies (\cite{Noeske:2007aa}). There is evidence that a
large fraction of the decline is associated with strongly
infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
decline does not appear to be due to the quenching of a large
fraction of the star-forming population, as reflected in observations
of the stellar mass function of quiescent and star-forming galaxies
(\citealt{Blanton:2006aa, bundy06a, borch06a, Moustakas:2013aa}).  These
findings leave little room for the participation of
environmentally-driven quenching in the global census of
star-formation.  As \cite{cooper08a} and others have pointed out,
because the environmental dependence of total star-formation rates at
fixed redshift is relatively small, environmentally effects are
unlikely to cause the overall star-formation rate decline.

Thus, the impact of environment on galaxy formation has to be
interpreted on top of the background of this overall decline affecting
galaxies in all environments. The most straightforward investigation
would be to directly determine the star-forming properties of galaxies as
a function of environment, stellar mass and redshift in a single,
consistently analyzed data set. This analysis can reveal how galaxies
are quenched in the universe over time, quantitatively establish the
contribution of environmental effects to the overall trends, and
reveal whether those trends happen equally in all environments.
However, such an analysis has not been done previously due to the lack
of sufficiently large samples. In this paper, we apply this approach
using the Prism Multi-object Survey (PRIMUS; \cite{Coil:2011aa}, 
\cite{Cool:2013aa}), the largest available redshift survey covering the epochs
between $0<z<1$.

In Section \ref{sec:sample} we present a brief description of the PRIMUS and SDSS data, our mass complete sample construction, and galaxy environment measurements. After dividing our galaxy sample into subsamples of star-forming or quiescent and high or low density environments, we compute and examine the evolution of the stellar mass functions for our subsamples in Section \ref{sec:smf}. Afterwards, in Section \ref{sec:qf_const}, we calculate the quiescent fraction, analyze the evolution of the quiescent fraction, quantify the effects of environment on the quiescent fraction evolution, and discuss the implications of our quiescent fraction results on star-formation quenching. Finally in Section \ref{sec:summary} we summarize our results.

Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70\;h\: \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$ with $h = 0.7$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SAMPLE SELECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on the evolution of the quenched fraction over the redshift range $0 < z < 1$. For our analysis, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis. In addition, we anchor our analysis at intermediate redshifts with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).

In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a brief summary of the PRIMUS data and the SDSS data used for our sample selection. Then in Section \ref{sec:target} we define our stellar mass complete galaxy sample. Afterwards, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming then calculate the environment using a volume-limited Environment Defining Population in Section \ref{sec:environment}. 
Finally in Section \ref{sec:edgeeffect}, we correct our galaxy sample and environment measurements for edge effects of the surveys.

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.2}
	\plotone{fig_edp_sdss_z0_05_0_12_primus_z0_2_1_0_Mr_redshift.png}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins: $z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, specified in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$. The survey was conducted using the IMACS spectrograph on the Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers (\citealt{Coil:2011aa, Cool:2013aa}).

@@

While the SDSS-{\em GALEX} data discussed above is derived from VAGC Data Release 7, since the release of the catalog, there have been significant improvements in the photometry. Notably, \cite{Blanton:2011aa} find that the background subtractions in SDSS Data Release 7 has a size dependent bias in the galaxy fluxes. In addition \cite{Bernardi:2013aa} find that the luminosity, and ultimately stellar mass, is underestimated when they are derived from the SDSS \texttt{cmodel} magnitudes in comparison to \texttt{PyMorph} single-S\'{e}rsic and Sersic-Exponential fits to the surface brightness profiles.

In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the improved background subtraction presented in \cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes. Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard VAGCVAGC photometry, we apply a preliminary correction to the stellar mass values obtained from \texttt{iSEDfit} assuming a consistent mass-to-light ratio. This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$; however, the effect of the mass correction was negligible for the quiescent fraction evolution results. As a result, we do not include the mass corrections and do not discuss the issues with photometric measurements any further in this paper. The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*} 
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{ccccccc} \hline \hline              
     &\multicolumn{1}{c}{$n_{\rm{env}}$}        & \multicolumn{2}{c}{$N_{\rm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\rm{lim}}$} & $M_{\rm{r}, lim}$ \\ 
    & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
$0.05 < z < 0.12$ & $n_{\rm{env}} < \lowenvthresh $ & 4969 & 5943 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.98 \\
               & $n_{\rm{env}} > \highenvthresh $ &17488 & 12244 &                          \\ 
                              & all          &$33968$                       & $30058$                          \\ \hline
$0.2 < z < 0.4$      &$n_{\rm{env}} < \lowenvthresh $           &282                    &1020 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.10 \\
               &$n_{\rm{env}} > \highenvthresh $            &410                    &850                           \\
               & all                & $995$                      & $2628$                          \\ \hline
$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh $           &426                       &1226 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -21.06 \\
               &$n_{\rm{env}} > \highenvthresh $            &543                       &983                           \\
               & all               & $1462$                      & $3334$                          \\ \hline
$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh $           &389                       &932  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.90 \\
               &$n_{\rm{env}} > \highenvthresh $            &642                       &907                           \\
               & all              & $1590$                      & $2852$                          \\ \hline
Total &      & \multicolumn{2}{c}{76887} & \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Number of galaxies ($N_{\rm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}). The subsamples are classified based on environment $n_{\rm{env}}$ and star formation rate (star-forming or quiescent). The lowest redshift bin is derived from SDSS; the rest are from PRIMUS. We also list the stellar mass completeness limit $\mathcal{M}_{\rm{lim}}$ for our sample and the $r$-band absolute magnitude limits $M_{\rm{r}, lim}$ for the Environment Defining Population. 
    \bigskip
\end{table*}

From the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data, in this section, we define our mass complete galaxy sample. We begin by imposing the parent sample selection criteria from \cite{Moustakas:2013aa}. More specifically, we take the statistically complete {\em primary} sample from the PRIMUS data (\citealt{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1. These limits are in different optical selection bands and have distinct values for the five PRIMUS target fields. We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$). Lastly, we impose a redshift range of $ 0.2 < z < 0.8$ for the PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations from sample variance and $ z < 0.8$ is selected due to the lack of sufficient statistics in subsamples defined below.

For the PRIMUS objects that meet the above criteria, we assign statistical weights (described in \citealt{Coil:2011aa} and \citealt{Cool:2013aa}) in order to correct for targeting incompleteness and redshift failures. The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
as in Equation (1) in \cite{Moustakas:2013aa}. Since we are ultimately interested in a mass complete galaxy sample to derive SMFs and QFs, next we impose stellar mass completeness limits to our galaxy sample.

>>>>

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael~Blanton\altaffilmark{1}, 
Alison~Coil\altaffilmark{2}, 
Richard~Cool\altaffilmark{3}, 
Daniel Eisenstein\altaffilmark{4},
John Moustakas\altaffilmark{5}, 
Ken Wong\altaffilmark{6}, 
Guangtun Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{3}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{5}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of
the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using
spectroscopic redshifts and multi-wavelength imaging data from the
PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey
(SDSS). Our stellar mass limited galaxy sample consists of $\sim
13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS
galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent
or star-forming based on an evolving specific star formation cut, and
as low or high density environments based on fixed cylindrical
aperture environment measurements on a volume-limited Environment
Defining Population (from PRIMUS and SDSS). For quiescent and
star-forming galaxies in low or high density environments, we examine
the evolution of their stellar mass function (SMF). Then using the
SMFs we compute $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify its
evolution within our redshift range. As expected, the quiescent
fraction is higher at higher masses and in denser environments. The
quiescent fraction rises with cosmic time for all masses and
environments. At a fiducial mass of $10^{10.5}M_\odot$, between $z\sim
0.7$ and $0.1$, the quiescent fraction's rise varies from 0.15 at the
lowest environments to 0.25 at the highest environments we measure.
These results suggest that for a minority of galaxies their cessation
of star formation might be associated with external influences on
them. However, in the recent Universe a substantial fraction of the
galaxies that cease forming stars do so due to internal processes.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their
star formation only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

@@

The most dramatic change in galaxy properties during the past eight
billion years has been a remarkable decline in the star-formation rate
of galaxies in the Universe (\citealt{hopkins06a}).  This decline
appears dominated by decreases in the rates of star-formation of
individual galaxies (\citealt{Noeske:2007aa}). There is evidence that
a large fraction of the decline is associated with strongly
infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
decline does not appear to be due to a complete cessation of star
formation for a large fraction of the star-forming population, as
reflected in observations of the stellar mass function of quiescent
and star-forming galaxies (\citealt{Blanton:2006aa, bundy06a,
  borch06a, Moustakas:2013aa}).  These findings leave little room for
the participation of environmentally-driven cessation of star
formation in the global census of star-formation.  As \cite{cooper08a}
and others have pointed out, because the environmental dependence of
total star-formation rates at fixed redshift is relatively small,
environmentally effects are unlikely to cause the overall
star-formation rate decline.

Thus, the impact of environment on galaxy formation has to be
interpreted on top of the background of this overall decline affecting
galaxies in all environments. The most straightforward investigation
would be to directly determine the star-forming properties of galaxies
as a function of environment, stellar mass and redshift in a single,
consistently analyzed data set. This analysis can reveal how galaxies
end their star formation over time, quantitatively establish the
contribution of environmental effects to the overall trends, and
reveal whether those trends happen equally in all environments.
However, such an analysis has not been done previously due to the lack
of sufficiently large samples. In this paper, we apply this approach
using the Prism Multi-object Survey (PRIMUS; \citealt{Coil:2011aa},
\citealt{Cool:2013aa}), the largest available redshift survey covering
the epochs between $0<z<1$.

In Section \ref{sec:sample} we present a brief description of the
PRIMUS and SDSS data, our mass complete sample construction, and
galaxy environment measurements. After dividing our galaxy sample into
subsamples of star-forming or quiescent and high or low density
environments, we compute and examine the evolution of the stellar mass
functions for our subsamples in Section \ref{sec:smf}. In
Section \ref{sec:qf_const}, we calculate the quiescent fraction,
analyze the evolution of the quiescent fraction, quantify the effects
of environment on the quiescent fraction evolution, and discuss the
implications of our quiescent fraction results on the cessation of
star-formation in galaxies. Finally in Section \ref{sec:summary} we
summarize our results.

Throughout the paper we assume a cosmology with $\Omega_{m} = 0.3,
\Omega_{\Lambda} = 0.7$, and $H_0 = 70 \: \rm{km} \; \rm{s}^{-1}
\rm{Mpc}^{-1}$. All magnitudes are AB-relative.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SAMPLE SELECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on
the evolution of the quiescent fraction over the redshift range $0 < z < 1$. For our analysis, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis. In addition, we anchor our analysis at intermediate redshifts with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).

In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a
brief summary of the PRIMUS data and the SDSS data used for our sample
selection.  In Section \ref{sec:sfq}, we classify our sample galaxies
as quiescent or star-forming.  In Section \ref{sec:target} we define
our stellar mass complete galaxy sample.  We calculate the environment
using a volume-limited Environment Defining Population in Section
\ref{sec:environment}.  Finally, in Section \ref{sec:edgeeffect}, we
account for edge effects in the surveys.

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.2}
	\plotone{fig_edp_sdss_z0_05_0_12_primus_z0_2_1_0_Mr_redshift.png}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins:$z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, specified in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and
spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim
120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range
$z \approx 0-1.2$. The survey was conducted using the IMACS
spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers (\citealt{Coil:2011aa, Cool:2013aa}).

@@

The SDSS-{\em GALEX} data discussed above is derived from the NYU-VAGC
based on SDSS Data Release 7, using the standard SDSS photometric
measurements. Several investigators have found that the background
subtraction techniques used in the standard photometric catalogs
introduce a size dependent bias in the galaxy fluxes and consequently
stellar masses (\citealt{west05a, blanton05b, lauer07a, bernardi07a,
  hyde09a, west10a}).

In order to quantify the effects of these photometric underestimations
in our analysis, we tried replacing our SDSS fluxes in the $ugriz$
band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog,
which incorporate the improved background subtraction presented in
\cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the
standard SDSS \texttt{cmodel} fluxes. Using the ratio of the
luminosity derived from the improved photometry over the luminosity
derived from the standard NYU-VAGC photometry, we apply a preliminary
correction to the stellar mass values obtained from \texttt{iSEDfit}
assuming a consistent mass-to-light ratio. This mass correction leads
to a significant increase in the stellar mass function for
$\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$; however, the effect of
the mass correction was negligible for the quiescent fraction
evolution results. As a result, for the results presented here we use
the standard SDSS fluxes and we do not discuss the issues with
photometric measurements any further in this paper. We note that a
thorough investigation of these issues to understand their effect on
the stellar mass function requires a reanalysis of both the SDSS
photometry and the deeper photometry used for PRIMUS targeting.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*} 
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{ccccccc} \hline \hline              
     &\multicolumn{1}{c}{$n_{\rm{env}}$}        & \multicolumn{2}{c}{$N_{\rm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\rm{lim}}$} & $M_{\rm{r}, lim}$ \\ 
    & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
$0.05 < z < 0.12$ & $n_{\rm{env}} < \lowenvthresh $ & 4969 & 5943 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.98 \\
               & $n_{\rm{env}} > \highenvthresh $ &17488 & 12244 &                          \\ 
                              & all          &$33968$                       & $30058$                          \\ \hline
$0.2 < z < 0.4$      &$n_{\rm{env}} < \lowenvthresh $           &282                    &1020 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.10 \\
               &$n_{\rm{env}} > \highenvthresh $            &410                    &850                           \\
               & all                & $995$                      & $2628$                          \\ \hline
$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh $           &426                       &1226 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -21.06 \\
               &$n_{\rm{env}} > \highenvthresh $            &543                       &983                           \\
               & all               & $1462$                      & $3334$                          \\ \hline
$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh $           &389                       &932  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.90 \\
               &$n_{\rm{env}} > \highenvthresh $            &642                       &907                           \\
               & all              & $1590$                      & $2852$                          \\ \hline
Total &      & \multicolumn{2}{c}{76887} & \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Number of galaxies ($N_{\rm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}). The subsamples are classified based on environment $n_{\rm{env}}$ and star formation rate (star-forming or quiescent). The lowest redshift bin is derived from SDSS; the rest are from PRIMUS. We also list the stellar mass completeness limit $\mathcal{M}_{\rm{lim}}$ for our sample and the $r$-band absolute magnitude limits $M_{\rm{r}, lim}$ for the Environment Defining Population. 
    \bigskip
\end{table*}

From the low redshift SDSS-{\em GALEX} and intermediate redshift
PRIMUS data we define our mass complete galaxy
sample. We begin by imposing the parent sample selection criteria from
\cite{Moustakas:2013aa}. More specifically, we take the statistically
complete {\em primary} sample from the PRIMUS data
(\citealt{Coil:2011aa}) and impose magnitude limits on optical
selection bands as specified in \cite{Moustakas:2013aa} Table 1. These
limits are in different optical selection bands and have distinct
values for the five PRIMUS target fields. We then exclude stars and
broad-line AGN to only select objects spectroscopically classified as
galaxies, with high-quality spectroscopic redshifts ($Q \geq
3$). Lastly, we impose a redshift range of $ 0.2 < z < 0.8$ for the
PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations
from sample variance and $ z < 0.8$ is selected due to the lack of
sufficient statistics in subsamples defined below.

For the PRIMUS objects that meet the above criteria, we assign statistical weights (described in \citealt{Coil:2011aa} and \citealt{Cool:2013aa}) in order to correct for targeting incompleteness and redshift failures. The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
as in Equation (1) in \cite{Moustakas:2013aa}.

Since we are ultimately interested in a mass complete galaxy sample to
derive SMFs and QFs, next we impose stellar mass completeness limits
to our galaxy sample.
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS are functions of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit. As in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits. For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4 (m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields. We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins. In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies. Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (star-forming or quiescent classification is described in the following section). Finally, we use the polynomials to obtain the minimum stellar masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$, which are then used as PRIMUS stellar mass completeness limits.
